---title:"Loading and Cleaning Data"
output:html_document---

# Introduction

Hi! This markdown file will walk you through the controls we're going to use for the project.

# Loading the package in the dev environment

I have put all the code into a package. You can use the load_all function from devtools to load it. If you make edits to the code, you have to reload the package and run the command again.

```{r}

devtools::load_all()

```

# Loading data

```{r}

rent_data <- readxl::read_xlsx("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/combined_dataset_no_controls.xlsx",
                               sheet = "LGA")

```

# Cleaning income and demographic data

```{r}
personal_income_statistics <- clean_personal_income_statistics("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/controls/income,earners by geography.xlsx")

demographic_statistics <- clean_demographic_statistics("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/controls/age and sex demographics.xlsx")

```
