---title:"Loading and Cleaning Data"
output:html_document---# Introduction

Hi! I've written up these documents to guide you through using our code-base. First, please load the data! Technically, in the ZIP file provided to you the raw data files will already be there so loading up the first chunk may not be necessary unless you want to check.

# Loading the package in the dev environment

I have put all the code into a package. You can use the load_all function from devtools to load it. If you make edits to the code, you have to reload the package but running the command again.

```{r}

devtools::load_all()

```

# Loading data

```{r}

# Don't forget to change the file path to a location you want to save the files to. You can also control left click on our custom functions to see the underlying code ! Please make sure that you use / instead of \ in the file path.

# PLEASE DO NOT RUN THIS IF YOU DO NOT WANT TO REDOWNLOAD THE NSW RAW DATA FILES.

download_nsw_datasets(file_path = "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/nsw")

# Note that for VIC there is only one data set you need to download from "https://discover.data.vic.gov.au/dataset/rental-report-quarterly-quarterly-median-rents-by-lga/resource/458264e7-0b2f-4061-80b4-c73ad4e94aa7" which makes things very easy. However, we had to make some manual adjustments to the sheet to make processing easier so the downloaded excel sheet won't match the one we have provided.

```

# Cleaning data

As we have downloaded the required files, we'll need to clean them, standardize their columns and join them together. NSW data is much harder to do than VIC.

## VIC data

```{r}

cleaned_vic_dataset <-  clean_vic_dataset("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/vic/VIC all quarters.xlsx")

writexl::write_xlsx(cleaned_vic_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_vic_dataset.xlsx")

```

## NSW data

```{r}

cleaned_nsw_dataset <- clean_nsw_datasets("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/nsw")

writexl::write_xlsx(cleaned_nsw_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_nsw_dataset.xlsx")

```

### Merging the two datasets

```{r}

combined_dataset <- dplyr::bind_rows(cleaned_nsw_dataset, cleaned_vic_dataset)

writexl::write_xlsx(combined_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/combined_dataset.xlsx")

```
