---title:"Loading and Cleaning Data"
output:html_document---

# Introduction

Hi! I've written up these documents to guide you through using our code-base. First, please load the data! Technically, in the ZIP file provided to you the raw data files will already be there so loading up the first chunk may not be necessary unless you want to check.

# Loading the package in the dev environment

I have put all the code into a package. You can use the load_all function from devtools to load it. If you make edits to the code, you have to reload the package and run the command again.

```{r}

devtools::load_all()

```

# Loading data

## Download NSW datasets

```{r}

# Don't forget to change the file path to a location you want to save the files to. You can also control left click on our custom functions to see the underlying code! Please make sure that you use / instead of \ in the file path.

# PLEASE DO NOT RUN THIS IF YOU DO NOT WANT TO REDOWNLOAD THE NSW RAW DATA FILES.

download_nsw_datasets(file_path = "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/nsw")

```

Note that:
1. For VIC there is only one data set you need to download from "https://discover.data.vic.gov.au/dataset/rental-report-quarterly-quarterly-median-rents-by-lga/resource/458264e7-0b2f-4061-80b4-c73ad4e94aa7" which makes things very easy. However, we had to make some manual adjustments to the sheet to make processing easier so the downloaded excel sheet won't match the one we have provided.
2. We only download 2018 datasets onwards as before 2017 they didn't publish the raw excel files and in 2017, the format was different/not standardised. This limits all other datasets to be from 2018 onwards.

## Download SA datasets

```{r}

# Don't forget to change the file path to a location you want to save the files to.

# PLEASE DO NOT RUN THIS IF YOU DO NOT WANT TO REDOWNLOAD THE SA RAW DATA FILES.

download_sa_datasets(file_path = "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/sa")

```

# Cleaning data

As we have downloaded the required files, we'll need to clean them, standardize their columns and join them together. NSW data is much harder to do than VIC.

## VIC data

```{r}

cleaned_vic_dataset <-  clean_vic_dataset("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/vic/VIC all quarters.xlsx")

writexl::write_xlsx(cleaned_vic_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_vic_dataset.xlsx")

```

Please note that we'll want all other datasets to only have observations for following combinations of dwelling and bedroom:
1. Flat with 1,2 or 3 bedrooms
2  House with 2,3 or 4 bedrooms
2. All Properties with all size bedrooms

I will just filter this at the end.

## NSW data

```{r}

cleaned_nsw_dataset <- clean_nsw_datasets("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/nsw")

writexl::write_xlsx(cleaned_nsw_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_nsw_dataset.xlsx")

```

## QLD data

```{r}

# Map these to ABS SA4 Regions manually as dataset doesn't contain a region column

cleaned_qld_dataset <- clean_qld_dataset("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/qld/rta-bond-statistics.xlsx")

writexl::write_xlsx(cleaned_qld_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_qld_dataset.xlsx")

```

## SA data

```{r}

# Map these to ABS SA4 Regions manually as dataset doesn't contain a region column

cleaned_sa_dataset <- clean_sa_datasets("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/sa") |>
  map_SA_LGA_to_region()

writexl::write_xlsx(cleaned_sa_dataset, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/cleaned_sa_dataset.xlsx")

```

### Merging the four datasets

```{r}

combined_dataset <- dplyr::bind_rows(cleaned_nsw_dataset, cleaned_vic_dataset, cleaned_sa_dataset, cleaned_qld_dataset)

max_year_and_quarter <- combined_dataset |>
  dplyr::group_by(State) |>
  dplyr::summarise(Max_Year = max(Year),
                   Max_Quarter = max(Quarter))

# As mentioned beforehand, NSW only has data available after 2018. Now, just find the common max year and quarter across all of the states. # Filter for common time period and required options

filtered_combined_dataset <- combined_dataset |>
  dplyr::filter(Year <= min(max_year_and_quarter$Max_Year) 
                & Quarter <= min(max_year_and_quarter$Max_Quarter),
                Year >= 2018,
                (Dwelling == "Flat" & Bedrooms %in% c(1, 2, 3)) |
                (Dwelling == "House" & Bedrooms %in% c(2, 3, 4)) |
                (Dwelling == "All Properties" & Bedrooms == "All Sizes")
                )

state_observations <- filtered_combined_dataset |>
  dplyr::filter(LGA == "Table Total") |>
  dplyr::select(-c(Region, LGA))

region_observations <- filtered_combined_dataset |>
  dplyr::filter(LGA == "Group Total") |>
  dplyr::select(-LGA)

LGA_observations <- filtered_combined_dataset |>
  dplyr::filter(LGA != "Group Total",
                LGA != "Table Total")

excel_file <- list(
  "State" = state_observations,
  "Region" = region_observations,
  "LGA" = LGA_observations
)

writexl::write_xlsx(excel_file, "C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/combined_dataset_no_controls.xlsx")

```   
