---title:"Loading and Cleaning Data"
output:html_document---

# Introduction

Hi! This markdown file will walk you through the controls we're going to use for the project.

# Loading the package in the dev environment

I have put all the code into a package. You can use the load_all function from devtools to load it. If you make edits to the code, you have to reload the package and run the command again.

```{r}

devtools::load_all()

```

# Loading data

```{r}


rent_data <- readxl::read_xlsx("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Cleaned Data/combined_dataset_no_controls.xlsx",
                               sheet = "LGA") |>
  dplyr::mutate(
    LGA = dplyr::replace_values(LGA, 
                                "Sydney City" ~ "Sydney", 
                                "Cootamundra-Gundagai Regional" ~ "Gundagai", 
                                "Sutherland" ~ "Sutherland Shire",
                                "The Hills" ~ "The Hills Shire",
                                "Bathurst" ~ "Bathurst Regional",
                                "Dubbo Regional" ~ "Western Plains Regional",
                                "Glen Innes" ~ "Glen Innes Severn",
                                "Greater Hume" ~ "Greater Hume Shire",
                                "Tamworth" ~ "Tamworth Regional",
                                "Upper Hunter" ~ "Upper Hunter Shire",
                                "Upper Lachlan" ~ "Upper Lachlan Shire",
                                "Warrumbungle" ~ "Warrumbungle Shire",
                                "Mornington Penin'a" ~ "Mornington Peninsula",
                                "Mallala" ~ "Adelaide Plains"
                                ) 
  )
```

They called:
1. Sydney, Sydney City in 2018 Q1, Q2
2. Gundagai, Cootamundra-Gundagai Regional in 2018 Q1, Q2
3. Sutherland Shire, Sutherland in 2018 Q1, Q2
4. The Hills Shire, The Hills in 2018 Q1, Q2
5. Bathurst Regional, Bathurst in 2018 Q1, Q2
6. Western Plains Regional, Dubbo Regional in 2018 Q1, Q2
7. Glen Innes Severn, Glen Innes in 2018 Q1, Q2
8. Greater Hume Shire, Greater Hume in 2018 Q1, Q2
9. Tamworth Regional, Tamworth in 2018 Q1, Q2
10. Upper Hunter Shire, Upper Hunter in 2018 Q1, Q2
11. Upper Lachlan Shire, Upper Lachlan in 2018 Q1, Q2
12. Warrambungle Shire, Warrambungle in 2018 Q1, Q2
13. Mornington Peninsula, Morningtong Penin'a throughout the entire dataset.
14. Adelaide Plains, Mallala in 2018 Q1, Q2
# Cleaning income and demographic data

```{r}
personal_income_statistics <- clean_personal_income_statistics("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/controls/income,earners by geography.xlsx")

demographic_statistics <- clean_demographic_statistics("C:/Users/David/Desktop/MicroEcon - Rent/RentAnalysis/Data/Raw Data/controls/age and sex demographics.xlsx")

test <- setdiff(rent_data$LGA, personal_income_statistics$LGA)
```

# Joining data and exporting 
```{r}

keys <- create_keys()

personal_income_statistics <- personal_income_statistics  |>
  dplyr::mutate(
    LGA = dplyr::replace_values(
      LGA,
      from = keys$income$matching_LGA_name_in_income_table,
      to = keys$income$rent_data_LGA_name_with_no_match
    )
  )  
test <- setdiff(rent_data$LGA, personal_income_statistics$LGA)
```


```{r}
controls <- list(
  personal_income_statistics,
  demographic_statistics
)

test <- setdiff(rent_data$LGA, personal_income_statistics$LGA)

final_data_with_controls <- join_controls(rent_data, controls)

```
